### 2021-06-01 paper/results.tex
Add figure labels and add figure with school scenarios.
Have observed and total new cases side by side for scenarios that involve testing.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/one_off_and_combined/full_new_known_case}
    \caption{The Effect of Each Channel on Observed New Cases Separately}
    \label{fig:}
    \figurenotes{\textcolor{red}{\ldots}}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\caption{The Effect of Different School Scenarios on Observed New Cases}
\label{fig:school_scenarios}
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/one_off_and_combined/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/one_off_and_combined/full_newly_infected}
\end{subfigure}
\caption{The Effect of Policies on Observed and Unobserved Cases}
\label{fig:explain_decline}
\figurenotes{\textcolor{red}{\ldots}}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/school_scenarios/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/school_scenarios/full_newly_infected}
\end{subfigure}
\caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
\figurenotes{\textcolor{red}{\ldots}}
\label{fig:school_scenarios}
\end{figure}

\FloatBarrier

\input{../figures/results/tables/student_infections_table}
